Supporting Information

### 2016-11-29 code/rmarkdown/article.Rmd
+ finalise ms format for mee submission

2. To address this issue, we developed the \\texttt{raptr R} package to guide reserve selection using targets for representing spatially explicit variables that underpin biodiversity processes as well as more typical area protection targets. Users set "amount targets"--similar to conventional methods--to secure a sufficient proportion of the features' geographic distributions. Additionally, users set "space targets" to secure a representative sample of variation in ecologically or evolutionary relevant attributes (eg. climatic or genetic variation). We demonstrate the functionality of this package using simulations and two case studies. We generate solutions using just amount targets--representing conventional methods--and compare them with solutions generated using amount and space targets.

@@

4. The \\texttt{raptr R} package provides a toolkit for making spatial conservation prioritizations that secure an adequate and representative sample of features. By targeting representativeness, prioritizations may have a greater chance of achieving long-term biodiversity persistence.

@@

\clearpage 
\input{./supporting-information.tex}

>>>>

2. To address this issue, we developed the \texttt{raptr R} package to guide reserve selection using targets for representing spatially explicit variables that underpin biodiversity processes as well as more typical area protection targets. Users set "amount targets"--similar to conventional methods--to secure a sufficient proportion of the features' geographic distributions. Additionally, users set "space targets" to secure a representative sample of variation in ecologically or evolutionary relevant attributes (eg. climatic or genetic variation). We demonstrate the functionality of this package using simulations and two case studies. We generate solutions using just amount targets--representing conventional methods--and compare them with solutions generated using amount and space targets.

@@

4. The \texttt{raptr R} package provides a toolkit for making spatial conservation prioritizations that secure an adequate and representative sample of features. By targeting representativeness, prioritizations may have a greater chance of achieving long-term biodiversity persistence.

@@

### 2016-11-29 code/rmarkdown/supporting-information.Rmd
+ finalise ms format for mee submission

---
bibliography: references.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
---
# Supporting Information

>>>>

---
title: "Supporting Information"
fontsize: 11pt
documentclass: article
subparagraph: true
bibliography: references.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
    includes:
      in_header: preamble.tex
---
